Elite individuals, insitutions, and economic growth accounting

### 2024-04-06 presentation/main.tex
only do PISA

    \begin{block}{Predicting missing values}
        XGBoost is a tree-based model that has built-in null handling. I use the remaining variables to predict school completion rates.
        Achieves significantly higher accuracy than linear regression.
    \end{block}

@@

\begin{frame}{Imputation results}
    \centering
    \includegraphics[width=\textwidth]{../build/xgboost.png}
\end{frame}

@@

\begin{frame}{Model specification}
    Let variables of interest be: $math99, ARWU, ARWU \times GDPpc, IMO$.
    For the sake of concision, let $E$ be a 1 by 4 matrix defined as:
    \[E_{i,t} = 
    \begin{bmatrix}
        math99_{i, t} & ARWU_{i, t} & ARWU_{i, t} \times GDPpc_{i, t} & IMO_{i, t}
    \end{bmatrix}
    \]
    Let the coefficients of $E_{i, t}$ be a 4 by 1 matrix called $\lambda$. For control variables, $C_{i, t}$ is the matrix of variables and $\alpha$ is coefficients..
    \begin{equation}
        Y_{i, t} = \beta_0 + \lambda E_{i, t} + \alpha C_{i, t} + T_t + \epsilon_{i, t}
    \end{equation}
    Due to missing data, consider another regression model which does not include $math99, math$:
    \begin{equation}
        Y_{i, t} = \alpha_0 + \lambda_{np} Enp_{i, t} + \alpha_{np} Cnp_{i, t} + T_t + \epsilon_{i, t}
    \end{equation}
    where $Y_{i,t}$ is GDP per capita growth in basis points. Time effects are included to control for secular changes (e.g. business cycles).
\end{frame}

\begin{frame}{Relationships}
    Insert scatter plots for each of 3 key variables.
\end{frame}

\begin{frame}{PISA data regression}{Highly dependent on model specification due to rich country bias and limited variation}
    \begin{table}[!htbp] \centering
        \resizebox{\linewidth}{!} {
            \begin{tabular}{@{\extracolsep{2pt}}lcccc}
                \\[-1.8ex]\hline
                \hline \\[-1.8ex]
                & \multicolumn{4}{c}{\textit{Dependent variable: GDPpcGrowth}} \
                \cr \cline{2-5}
                \\[-1.8ex] & (1) & (2) & (3) & (4) \\
                \hline \\[-1.8ex]
                 PISA Math in global P99 & & 12.582$^{}$ & 16.888$^{}$ & 122.288$^{}$ \\
                & & (23.160) & (20.869) & (79.814) \\
                 IMO score per log population & 11.744$^{}$ & 4.247$^{}$ & 10.055$^{}$ & 71.462$^{**}$ \\
                & (7.232) & (9.102) & (8.154) & (29.447) \\
                 ARWU insitutions & -586.307$^{***}$ & -559.067$^{**}$ & -575.550$^{***}$ & -295.306$^{}$ \\
                & (198.985) & (240.047) & (213.365) & (559.483) \\
                 ARWU insitutions x GDP PC & 0.009$^{**}$ & 0.009$^{*}$ & 0.008$^{*}$ & -0.007$^{}$ \\
                & (0.004) & (0.005) & (0.004) & (0.014) \\
                 PISA Math & & 0.636$^{}$ & -0.273$^{}$ & -4.581$^{}$ \\
                & & (0.949) & (0.876) & (3.456) \\
                 GDP per capita & -0.003$^{**}$ & -0.006$^{***}$ & -0.004$^{**}$ & -0.007$^{}$ \\
                & (0.002) & (0.002) & (0.002) & (0.012) \\
                 Primary School Completion Rate & -0.712$^{}$ & -2.406$^{}$ & -0.112$^{}$ & -4.624$^{}$ \\
                & (3.868) & (4.849) & (4.338) & (18.411) \\
                 Lower Sec. Completion Rate & 1.485$^{}$ & 0.777$^{}$ & 1.568$^{}$ & 21.092$^{}$ \\
                & (3.255) & (3.704) & (3.290) & (16.364) \\
                 Upper Sec. Completion Rate & 1.597$^{}$ & 1.439$^{}$ & 1.542$^{}$ & -15.224$^{}$ \\
                & (2.515) & (2.870) & (2.543) & (17.185) \\
                 Democracy Rating & 0.940$^{}$ & 3.972$^{}$ & 4.167$^{}$ & -12.702$^{}$ \\
                & (19.787) & (23.684) & (21.249) & (128.289) \\
                 Time Effects & Yes & No & Yes & Yes \\
                 Fixed Effects & No & No & No & Yes \\
                 Entities & 48 & 48 & 48 & 48 \\
                \hline \\[-1.8ex]
                 Observations & 109 & 109 & 109 & 109 \\
                 $R^2$ & 0.397 & 0.212 & 0.402 & 0.753 \\
                 Adjusted $R^2$ & 0.322 & 0.122 & 0.313 & 0.432 \\
                 Residual Std. Error & 197.737 (df=96) & 224.993 (df=97) & 199.076 (df=94) & 181.047 (df=47) \\
                 F Statistic & 5.275$^{***}$ (df=12; 96) & 2.367$^{**}$ (df=11; 97) & 4.512$^{***}$ (df=14; 94) & 2.345$^{***}$ (df=61; 47) \\
                \hline
                \hline \\[-1.8ex]
                \textit{Note:} & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
                \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{Interpreting Regressions}{PISA regressions}
    Regression results do not present a clear picture of the existence of a statistical relationship between elite indicators and economic growth.
    \begin{block}{Little variation in data}
        \begin{itemize}
            \item Countries and regions with PISA test scores tend to be wealthier, more developed economies
            \item Low variance within countries over time and between countries as a result
        \end{itemize}
    \end{block}

@@

\begin{frame}
    \frametitle{Non-PISA data regression}
    \begin{table}[!htbp] \centering
        \resizebox{\linewidth}{!} {
            \begin{tabular}{@{\extracolsep{5pt}}lcccc}
                \\[-1.8ex]\hline
                \hline \\[-1.8ex]
                & \multicolumn{4}{c}{\textit{Dependent variable: GDPpcGrowth}} \
                \cr \cline{2-5}
                \\[-1.8ex] & \multicolumn{1}{c}{Model 3 (PISA)} & \multicolumn{1}{c}{Model 5 (PISA years)} & \multicolumn{1}{c}{Model 6 (All years)} & \multicolumn{1}{c}{Model 7 (All years, FE)}  \\
                \hline \\[-1.8ex]
                 IMO score per log population & 10.055$^{}$ & 18.160$^{***}$ & 13.297$^{***}$ & 10.006$^{}$ \\
                & (8.154) & (6.517) & (3.993) & (10.776) \\
                 ARWU insitutions & -575.550$^{***}$ & -446.996$^{**}$ & -353.730$^{***}$ & 523.241$^{*}$ \\
                & (213.365) & (221.189) & (131.179) & (292.381) \\
                 ARWU insitutions x GDP PC & 0.008$^{*}$ & 0.008$^{*}$ & 0.005$^{*}$ & -0.012$^{**}$ \\
                & (0.004) & (0.004) & (0.002) & (0.006) \\
                 GDP per capita & -0.004$^{**}$ & -0.005$^{***}$ & -0.004$^{***}$ & 0.002$^{}$ \\
                & (0.002) & (0.002) & (0.001) & (0.004) \\
                 Primary School Completion Rate & -0.112$^{}$ & -3.530$^{**}$ & -1.754$^{}$ & -1.505$^{}$ \\
                & (4.338) & (1.740) & (1.227) & (4.983) \\
                 Lower Sec. Completion Rate & 1.568$^{}$ & 5.370$^{**}$ & 1.911$^{}$ & -0.147$^{}$ \\
                & (3.290) & (2.445) & (1.692) & (5.035) \\
                 Upper Sec. Completion Rate & 1.542$^{}$ & -2.365$^{}$ & 0.081$^{}$ & 1.981$^{}$ \\
                & (2.543) & (1.946) & (1.325) & (3.776) \\
                 Democracy Rating & 4.167$^{}$ & 13.397$^{}$ & 19.784$^{***}$ & 87.626$^{**}$ \\
                & (21.249) & (11.913) & (7.637) & (37.349) \\
                 Population & -0.000$^{*}$ & -0.000$^{}$ & -0.000$^{}$ & 0.000$^{}$ \\
                & (0.000) & (0.000) & (0.000) & (0.000) \\
                 Time Effects & Yes & Yes & Yes & Yes \\
                 Fixed Effects & No & No & No & Yes \\
                 Entities & 48 & 103 & 137 & 137 \\
                \hline \\[-1.8ex]
                 Observations & 109 & 222 & 746 & 746 \\
                 $R^2$ & 0.402 & 0.202 & 0.380 & 0.611 \\
                 Adjusted $R^2$ & 0.313 & 0.156 & 0.360 & 0.505 \\
                 Residual Std. Error & 199.076 (df=94) & 240.456 (df=209) & 288.864 (df=722) & 253.976 (df=586) \\
                 F Statistic & 4.512$^{***}$ (df=14; 94) & 4.417$^{***}$ (df=12; 209) & 19.219$^{***}$ (df=23; 722) & 5.785$^{***}$ (df=159; 586) \\
                \hline
                \hline \\[-1.8ex]
                \textit{Note:} & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
            \end{tabular}
        }
        \end{table}
\end{frame}

>>>>

    \begin{block}{Predicting missing values}
        XGBoost is a tree-based model that has built-in null handling. I use the remaining variables to predict school completion rates and EIU democracy scores.
        Achieves significantly higher accuracy than linear regression.
    \end{block}

@@

\begin{frame}{Imputation results}{School completion rates}
    \centering
    \includegraphics[width=\textwidth]{../build/xgboost.png}
\end{frame}

\begin{frame}{Imputation results}{EIU Democracy Score}
    \centering
    \includegraphics[width=\textwidth]{../build/eiu_xgboost.png}
\end{frame}

@@

\begin{frame}{Model specification}
    Let elite indicators be: $math99, ARWU, IMO$.
    For the sake of concision, let $E_{i,t}$ be a 1 by 4 matrix defined as:
    \[E_{i,t} = 
    \begin{bmatrix}
        math99_{i, t} & ARWU_{i, t} & ARWU_{i, t} \times GDPpc_{i, t} & IMO_{i, t}
    \end{bmatrix}
    \] for country/region $i$ in year $t$.
    Let the coefficients of $E_{i, t}$ be a 4 by 1 matrix called $\lambda$. For control variables, $I_{i, t}$ is the matrix of variables and $\alpha$ is coefficients.
    \begin{equation}
        Y_{i, t} = \beta_0 + \lambda E_{i, t} + \delta GDPpc \times E_{i,t} + \alpha I_{i, t} + T_t + C_i + \epsilon_{i, t}
    \end{equation}
    where $T,C$ represent time and entity dummies respectively and $Y_{i,t}$ be the GDP per capita growth in basis points for a country/region $i$ and year $t$.
\end{frame}

\begin{frame}{Relationships}
    \centering
    \includegraphics[width=\textwidth]{../charts/relationships.png}
\end{frame}

\begin{frame}{PISA panel regression}{Highly dependent on model specification due to rich country bias and limited variation}
    \begin{table}[!htbp] \centering
        \resizebox{\linewidth}{!} {
            \begin{tabular}{@{\extracolsep{5pt}}lcccc}
                \\[-1.8ex]\hline
                \hline \\[-1.8ex]
                & \multicolumn{4}{c}{\textit{Dependent variable: GDP Per Capita Growth (bps)}} \
                \cr \cline{2-5}
                \\[-1.8ex] & \multicolumn{1}{c}{Model 1 (base)} & \multicolumn{1}{c}{Model 2} & \multicolumn{1}{c}{Model 3 (Time FE)} & \multicolumn{1}{c}{Model 4 (Time + Entity FE)}  \\
                \hline \\[-1.8ex]
                 PISA Math in global P99 & & -43.491$^{}$ & -40.291$^{}$ & -126.152$^{*}$ \\
                & & (48.245) & (40.349) & (64.627) \\
                 PISA Math 99 x GDP PC & & 0.000$^{}$ & 0.000$^{}$ & 0.001$^{}$ \\
                & & (0.001) & (0.001) & (0.001) \\
                 IMO score per log population & 6.604$^{}$ & 3.629$^{}$ & 4.581$^{}$ & 20.285$^{}$ \\
                & (8.473) & (10.582) & (8.833) & (21.169) \\
                 IMO score x GDP pc & -0.000$^{}$ & 0.000$^{}$ & -0.000$^{}$ & -0.001$^{*}$ \\
                & (0.000) & (0.000) & (0.000) & (0.000) \\
                 ARWU insitutions & -588.767$^{***}$ & -538.997$^{***}$ & -580.030$^{***}$ & -764.617$^{***}$ \\
                & (135.656) & (178.746) & (149.452) & (250.804) \\
                 ARWU insitutions x GDP PC & 0.009$^{***}$ & 0.008$^{**}$ & 0.009$^{***}$ & 0.011$^{***}$ \\
                & (0.003) & (0.003) & (0.003) & (0.004) \\
                 PISA Math & & 1.150$^{}$ & 0.908$^{}$ & 0.495$^{}$ \\
                & & (0.792) & (0.732) & (1.761) \\
                 GDP per capita & -0.003$^{**}$ & -0.003$^{*}$ & -0.003$^{**}$ & 0.000$^{}$ \\
                & (0.001) & (0.002) & (0.001) & (0.005) \\
                 Primary School Completion Rate & -3.554$^{}$ & -11.911$^{***}$ & -5.387$^{}$ & -4.028$^{}$ \\
                & (3.345) & (4.157) & (3.602) & (4.947) \\
                 Lower Sec. Completion Rate & -1.475$^{}$ & -0.571$^{}$ & -1.291$^{}$ & -0.446$^{}$ \\
                & (2.945) & (3.540) & (2.948) & (4.443) \\
                 Upper Sec. Completion Rate & 5.643$^{**}$ & 6.665$^{**}$ & 5.385$^{**}$ & 3.364$^{}$ \\
                & (2.343) & (2.835) & (2.354) & (3.692) \\
                 Democracy Rating & -1.606$^{}$ & 2.270$^{}$ & -7.429$^{}$ & 36.204$^{}$ \\
                & (13.894) & (17.254) & (14.431) & (61.854) \\
                 Time Effects & Yes & No & Yes & Yes \\
                 Fixed Effects & No & No & No & Yes \\
                 Entities & 89 & 89 & 89 & 89 \\
                \hline \\[-1.8ex]
                 Observations & 440 & 440 & 440 & 440 \\
                 $R^2$ & 0.388 & 0.092 & 0.392 & 0.567 \\
                 Adjusted $R^2$ & 0.364 & 0.064 & 0.364 & 0.428 \\
                 Residual Std. Error & 360.908 (df=423) & 437.923 (df=426) & 360.976 (df=420) & 342.461 (df=332) \\
                 F Statistic & 16.727$^{***}$ (df=16; 423) & 3.314$^{***}$ (df=13; 426) & 14.230$^{***}$ (df=19; 420) & 4.066$^{***}$ (df=107; 332) \\
                \hline
                \hline \\[-1.8ex]
                \textit{Note:} & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
                \end{tabular}
        }
        \end{table}
\end{frame}

\begin{frame}{PISA yearly regression}
    \begin{table}[!htbp] \centering
        \resizebox{\linewidth}{!} {
            \begin{tabular}{@{\extracolsep{1pt}}lcccccccc}
                \\[-1.8ex]\hline
                \hline \\[-1.8ex]
                & \multicolumn{8}{c}{\textit{Dependent variable: GDP Per Capita Growth (bps)}} \
                \cr \cline{2-9}
                \\[-1.8ex] & \multicolumn{1}{c}{2003} & \multicolumn{1}{c}{2006} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2012} & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2018} & \multicolumn{1}{c}{2022} & \multicolumn{1}{c}{Panel FE}  \\
                \hline \\[-1.8ex]
                 PISA Math in global P99 & -36.263$^{}$ & -323.594$^{**}$ & 128.012$^{}$ & -57.807$^{}$ & 466.275$^{**}$ & -13.249$^{}$ & -185.929$^{**}$ & -126.152$^{*}$ \\
                & (92.257) & (138.527) & (134.080) & (93.739) & (198.856) & (80.330) & (75.932) & (64.627) \\
                 PISA Math 99 x GDP PC & -0.000$^{}$ & 0.004$^{}$ & 0.001$^{}$ & 0.001$^{}$ & -0.009$^{**}$ & 0.000$^{}$ & 0.002$^{}$ & 0.001$^{}$ \\
                & (0.002) & (0.003) & (0.003) & (0.002) & (0.004) & (0.001) & (0.001) & (0.001) \\
                 IMO score per log population & 5.787$^{}$ & 13.706$^{}$ & 7.250$^{}$ & 9.955$^{}$ & 27.849$^{}$ & 2.586$^{}$ & -10.574$^{}$ & 20.285$^{}$ \\
                & (24.329) & (28.793) & (25.375) & (20.089) & (37.305) & (10.918) & (18.736) & (21.169) \\
                 IMO score x GDP pc & -0.000$^{}$ & -0.001$^{}$ & 0.000$^{}$ & 0.000$^{}$ & -0.001$^{}$ & -0.000$^{}$ & 0.000$^{}$ & -0.001$^{*}$ \\
                & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.000) & (0.000) & (0.000) \\
                 ARWU insitutions & -461.941$^{}$ & -374.847$^{}$ & 298.772$^{}$ & -746.052$^{**}$ & -1132.300$^{}$ & -365.119$^{}$ & -1310.810$^{***}$ & -764.617$^{***}$ \\
                & (443.713) & (420.235) & (453.763) & (292.719) & (718.477) & (288.492) & (455.353) & (250.804) \\
                 ARWU insitutions x GDP PC & 0.004$^{}$ & 0.001$^{}$ & -0.004$^{}$ & 0.008$^{}$ & 0.030$^{**}$ & 0.006$^{}$ & 0.013$^{}$ & 0.011$^{***}$ \\
                & (0.011) & (0.009) & (0.009) & (0.005) & (0.014) & (0.004) & (0.008) & (0.004) \\
                 PISA Math & 0.436$^{}$ & 6.935$^{***}$ & -6.860$^{***}$ & 0.324$^{}$ & -1.519$^{}$ & 1.177$^{}$ & 2.807$^{}$ & 0.495$^{}$ \\
                & (1.552) & (1.906) & (2.386) & (1.489) & (2.828) & (1.002) & (2.056) & (1.761) \\
                 GDP per capita & -0.006$^{}$ & -0.005$^{}$ & -0.000$^{}$ & -0.003$^{}$ & 0.002$^{}$ & -0.007$^{***}$ & -0.003$^{}$ & 0.000$^{}$ \\
                & (0.005) & (0.005) & (0.006) & (0.002) & (0.005) & (0.002) & (0.004) & (0.005) \\
                 Primary School Completion Rate & 7.306$^{}$ & -11.680$^{}$ & 4.589$^{}$ & -15.665$^{}$ & -4.820$^{}$ & -8.787$^{}$ & 4.752$^{}$ & -4.028$^{}$ \\
                & (4.789) & (10.409) & (13.405) & (9.658) & (14.437) & (5.579) & (9.745) & (4.947) \\
                 Lower Sec. Completion Rate & 4.652$^{}$ & 7.506$^{}$ & -0.454$^{}$ & 2.430$^{}$ & -1.228$^{}$ & 6.617$^{*}$ & -13.439$^{}$ & -0.446$^{}$ \\
                & (6.867) & (8.157) & (8.302) & (5.785) & (10.676) & (3.951) & (8.396) & (4.443) \\
                 Upper Sec. Completion Rate & 4.916$^{}$ & 3.930$^{}$ & -2.992$^{}$ & 5.781$^{}$ & 4.631$^{}$ & 0.908$^{}$ & 10.924$^{*}$ & 3.364$^{}$ \\
                & (7.172) & (6.850) & (7.450) & (4.375) & (8.029) & (3.174) & (6.081) & (3.692) \\
                 Democracy Rating & -91.681$^{**}$ & -148.435$^{**}$ & 59.739$^{}$ & 36.375$^{}$ & 25.423$^{}$ & 15.183$^{}$ & -5.316$^{}$ & 36.204$^{}$ \\
                & (39.476) & (56.849) & (46.067) & (30.648) & (51.072) & (16.370) & (28.766) & (61.854) \\
                \hline \\[-1.8ex]
                 Observations & 40 & 56 & 69 & 61 & 65 & 73 & 76 & 440 \\
                 $R^2$ & 0.677 & 0.536 & 0.268 & 0.363 & 0.267 & 0.343 & 0.477 & 0.567 \\
                 Adjusted $R^2$ & 0.516 & 0.392 & 0.095 & 0.187 & 0.081 & 0.198 & 0.368 & 0.428 \\
                 Residual Std. Error & 188.826 (df=26) & 363.704 (df=42) & 411.759 (df=55) & 250.551 (df=47) & 455.710 (df=51) & 178.763 (df=59) & 325.047 (df=62) & 342.461 (df=332) \\
                 F Statistic & 4.193$^{***}$ (df=13; 26) & 3.732$^{***}$ (df=13; 42) & 1.547$^{}$ (df=13; 55) & 2.060$^{**}$ (df=13; 47) & 1.432$^{}$ (df=13; 51) & 2.365$^{**}$ (df=13; 59) & 4.353$^{***}$ (df=13; 62) & 4.066$^{***}$ (df=107; 332) \\
                \hline
                \hline \\[-1.8ex]
                \textit{Note:} & \multicolumn{8}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
                \end{tabular}
        }
        \end{table}

% \begin{frame}
%     \frametitle{Non-PISA data regression}
%     \begin{table}[!htbp] \centering
%         \resizebox{\linewidth}{!} {
%             \begin{tabular}{@{\extracolsep{5pt}}lcccc}
%                 \\[-1.8ex]\hline
%                 \hline \\[-1.8ex]
%                 & \multicolumn{4}{c}{\textit{Dependent variable: GDPpcGrowth}} \
%                 \cr \cline{2-5}
%                 \\[-1.8ex] & \multicolumn{1}{c}{Model 3 (PISA)} & \multicolumn{1}{c}{Model 5 (PISA years)} & \multicolumn{1}{c}{Model 6 (All years)} & \multicolumn{1}{c}{Model 7 (All years, FE)}  \\
%                 \hline \\[-1.8ex]
%                  IMO score per log population & 10.055$^{}$ & 18.160$^{***}$ & 13.297$^{***}$ & 10.006$^{}$ \\
%                 & (8.154) & (6.517) & (3.993) & (10.776) \\
%                  ARWU insitutions & -575.550$^{***}$ & -446.996$^{**}$ & -353.730$^{***}$ & 523.241$^{*}$ \\
%                 & (213.365) & (221.189) & (131.179) & (292.381) \\
%                  ARWU insitutions x GDP PC & 0.008$^{*}$ & 0.008$^{*}$ & 0.005$^{*}$ & -0.012$^{**}$ \\
%                 & (0.004) & (0.004) & (0.002) & (0.006) \\
%                  GDP per capita & -0.004$^{**}$ & -0.005$^{***}$ & -0.004$^{***}$ & 0.002$^{}$ \\
%                 & (0.002) & (0.002) & (0.001) & (0.004) \\
%                  Primary School Completion Rate & -0.112$^{}$ & -3.530$^{**}$ & -1.754$^{}$ & -1.505$^{}$ \\
%                 & (4.338) & (1.740) & (1.227) & (4.983) \\
%                  Lower Sec. Completion Rate & 1.568$^{}$ & 5.370$^{**}$ & 1.911$^{}$ & -0.147$^{}$ \\
%                 & (3.290) & (2.445) & (1.692) & (5.035) \\
%                  Upper Sec. Completion Rate & 1.542$^{}$ & -2.365$^{}$ & 0.081$^{}$ & 1.981$^{}$ \\
%                 & (2.543) & (1.946) & (1.325) & (3.776) \\
%                  Democracy Rating & 4.167$^{}$ & 13.397$^{}$ & 19.784$^{***}$ & 87.626$^{**}$ \\
%                 & (21.249) & (11.913) & (7.637) & (37.349) \\
%                  Population & -0.000$^{*}$ & -0.000$^{}$ & -0.000$^{}$ & 0.000$^{}$ \\
%                 & (0.000) & (0.000) & (0.000) & (0.000) \\
%                  Time Effects & Yes & Yes & Yes & Yes \\
%                  Fixed Effects & No & No & No & Yes \\
%                  Entities & 48 & 103 & 137 & 137 \\
%                 \hline \\[-1.8ex]
%                  Observations & 109 & 222 & 746 & 746 \\
%                  $R^2$ & 0.402 & 0.202 & 0.380 & 0.611 \\
%                  Adjusted $R^2$ & 0.313 & 0.156 & 0.360 & 0.505 \\
%                  Residual Std. Error & 199.076 (df=94) & 240.456 (df=209) & 288.864 (df=722) & 253.976 (df=586) \\
%                  F Statistic & 4.512$^{***}$ (df=14; 94) & 4.417$^{***}$ (df=12; 209) & 19.219$^{***}$ (df=23; 722) & 5.785$^{***}$ (df=159; 586) \\
%                 \hline
%                 \hline \\[-1.8ex]
%                 \textit{Note:} & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\
%             \end{tabular}
%         }
%         \end{table}
% \end{frame}

\begin{frame}{Interpretation}
    \begin{block}{IMO Scores}
        \begin{itemize}
            \item Mostly indicates positive main relationship with GDP per capita growth, but negative interaction with GDP per capita.
            \item Suggests that lower income countries may see more benefit to what IMO scores are a proxy of (non-causal)
        \end{itemize}
    \end{block}

    \begin{block}{PISA math 99 percentile share}
        \begin{itemize}
            \item Very sensitive to model specification and changes between years
            \item Negative main effect but positive interaction effect
        \end{itemize}
    \end{block}

    \begin{block}{ARWU insitutions per million}
        \begin{itemize}
            \item Consistent negative main effect, but positive interaction effect with GDP per capita
            \item Can interpret as OVB, or that higher income countries may see more use from high-ranking institutions
        \end{itemize}
    \end{block}

\begin{frame}{Limitations: data sample problems}
    Regression results do not present a clear picture of the existence of a statistical relationship between elite indicators and economic growth.
    \begin{block}{Little variation in data}
        \begin{itemize}
            \item Countries and regions with PISA test scores tend to be wealthier, more developed economies
            \item Low variance within countries over time and between countries as a result
        \end{itemize}
    \end{block}

@@

\begin{frame}{Limitations: Yearly vs. Panel}{Significant year-to-year variation}
    \begin{block}{Unstable panel vs. yearly results}
        The panel methods mask some of the year-to-year changes in relationships.
        Some indicators are more stable than others, but $math99$ in particular alternates from positive to negative coefficient with large swings.
    \end{block}

    \begin{block}{Omitted Variable Bias}
        Large changes in relationship magnitude and direction suggests that omitted variable bias is a big problem.
    \end{block}
